Documentation FFI Sonar Simulator

### 2013-05-15 FFI-Simulator/ffi-simulator.tex
...
la2pdf commit - 2013:05:15	18:25:05	(Wed15.May)

{\Large Design Suggestion}\\[0.2cm]
{\itshape for a}\\[0.2cm]
{\Large GPU Based Sonar Template Simulator}\\[2cm]
{\itshape by}\\[0.2cm]
\begin{minipage}{0.35\textwidth}\small\centering
Jo Inge \textsc{Buskenes}\\
\textnormal{\color{SeaGreen}joibu (at) ifi.uio.no}
\end{minipage}
\begin{minipage}{0.35\textwidth}\small\centering
Jon Petter \textsc{Åsen}\\
\textnormal{\color{SeaGreen}jpaasen (at) ifi.uio.no}
\end{minipage}\\[2cm]
{\itshape on the behalf of}\\[0.2cm]
\begin{minipage}[t]{0.49\textwidth}\centering
  \centering\includegraphics[height=3cm]{gfx/FFILogo.png}\\
  \textsc{The Norwegian Defence Research Establishment (FFI)}
\end{minipage}\\[0.5cm]
\begin{minipage}[t]{0.4\textwidth}\small\centering
Øivind \textsc{Midtgård}\\
\textnormal{\color{SeaGreen}oivind.midtgaard (at) ffi.no}
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}\small\centering
Herman \textsc{Midelfart}\\
\textnormal{\color{SeaGreen}herman.midelfart (at) ffi.no}
\end{minipage}\\[0.3cm]
\begin{minipage}{0.32\textwidth}\small\centering
Roy Edgar \textsc{Hansen}\\
\textnormal{\color{SeaGreen}roy-edgar.hansen (at) ffi.no}
\end{minipage}
\vfill
\small
\today
\end{center}

@@

The way we see it, there are two possible approaches to implementing the mentioned simulator (figure \ref{implementation}). One can either

@@

\begin{itemize0}
\item use OpenGL to produce depth-maps of the scene, and CUDA to illuminate it as a sonar would, or
\item use OpenGL to render the full scene with lighting.
\end{itemize0}

In either case the simulator will take a seafloor and target model as input, and generate a simulated sonar image. To offload the CPU further, the GPU can then proceed to compute the correlation between the template and the isolated image segment, and an image mask. This should be fairly easy to implement, will compute efficiently on the GPU, and allows us to avoid sending each template back to the CPU over the limited bandwidth CPU$\leftrightarrow$GPU bus. Note that these steps will have to be carried out in CUDA regardless of the approach selected.

@@

When we wish to set up a 3D scene, move objects and cameras around, and render it using a GPU, it is better to use e.g. OpenGL than CUDA. OpenGL was made for this specific task, is cross-platform, feature-rich and well-matured. By looking at the graphics quality and frame-rates displayed by modern OpenGL-based games it should also be fairly straight-forward to get the performance we need out of this library.

@@

The main advantage of the CUDA implementation lies in its flexibility. If desired, it can be modified to handle sound propagation in non-ideal mediums, penetrable objects, signal multipath, diffraction and phase-dependent effects such as speckle. However, this will also lead to increased code complexity and development time, and  will naturally increase. However, we expect that such features will be more realizable in CUDA than OpenGL.

@@

\end{document}

>>>>

{\Large Design Suggestion} v2\\[0.2cm]
{\itshape for a}\\[0.2cm]
{\Large GPU Based Sonar Template Simulator}\\[2cm]
{\itshape by}\\[0.2cm]
\begin{minipage}{0.35\textwidth}\small\centering
Jo Inge \textsc{Buskenes}\\
\textnormal{\color{SeaGreen}joibu (at) ifi.uio.no}
\end{minipage}
\begin{minipage}{0.35\textwidth}\small\centering
Jon Petter \textsc{Åsen}\\
\textnormal{\color{SeaGreen}jpaasen (at) ifi.uio.no}
\end{minipage}\\[2cm]
{\itshape on the behalf of}\\[0.2cm]
\begin{minipage}[t]{0.49\textwidth}\centering
  \centering\includegraphics[height=3cm]{gfx/FFILogo.png}\\
  \textsc{The Norwegian Defence Research Establishment (FFI)}
\end{minipage}\\[0.5cm]
\begin{minipage}[t]{0.4\textwidth}\small\centering
Øivind \textsc{Midtgård}\\
\textnormal{\color{SeaGreen}oivind.midtgaard (at) ffi.no}
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}\small\centering
Herman \textsc{Midelfart}\\
\textnormal{\color{SeaGreen}herman.midelfart (at) ffi.no}
\end{minipage}\\[0.3cm]
\begin{minipage}{0.32\textwidth}\small\centering
Roy Edgar \textsc{Hansen}\\
\textnormal{\color{SeaGreen}roy-edgar.hansen (at) ffi.no}
\end{minipage}
\vfill
\small
\today
\end{center}

@@

In the original specification we put forth two possible approaches to implementing the mentioned simulator (figure \ref{implementation}). We envisioned to either

@@

\begin{itemize0}
\item use OpenGL to produce depth-maps of the scene, and CUDA/OpenCL to illuminate it as a sonar would, or
\item use OpenGL to render the full scene with lighting.
\end{itemize0}

In each of these cases the simulator takes a seafloor and target model as input, and generates a simulated sonar image.

We believe the first alternative is the more customizable of the two, and the second being the least complex to implement.

To further offload the CPU, the GPU could proceed to compute the correlation between the template and the isolated image segment, and an image mask. The advantages included a fairly straight forward implementation that would compute efficiently on the GPU,

 and allows us to avoid sending each template back to the CPU over the limited bandwidth CPU$\leftrightarrow$GPU bus. Note that these steps will have to be carried out in CUDA regardless of the approach selected.

@@

When we wish to set up a 3D scene, move objects and cameras around, and render it using a GPU, it is better to use e.g. OpenGL than CUDA/OpenGL. OpenGL was made for this specific task, is cross-platform, feature-rich and well-matured. By looking at the graphics quality and frame-rates displayed by modern OpenGL-based games it should also be fairly straight-forward to get the performance we need out of this library.

@@

The main advantage of the CUDA implementation lies in its flexibility. If desired, it can be modified to handle sound propagation in non-ideal mediums, penetrable objects, signal multipath, diffraction and phase-dependent effects such as speckle. The drawback is the added code complexity and development time.

@@

% \section{Documentation}

% \input{ffi-documentation}
\end{document}
